Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
minor edit
correction to rts algorithm

\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix } \\

@@

\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute}\\

@@

is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix~\ref{ap:Lowerbound} )  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.  $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$). Note that this is actually the smoother output.

>>>>

\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t\in\left\lbrace 0,\cdots,T-1\right\rbrace $, calculate the predicted state and the predicted covariance matrix } \\

@@

\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,1\right\rbrace $ compute}\\

@@

is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix~\ref{ap:Lowerbound} )  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.  $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$). Note that this is actually the smoother output which is obtained at the E-step.
